### 2021-03-04 background.tex
second general review

A sandbox is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries, like the file system, the network, or other device data. It enables testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device that runs the application. This need may arise in a variety of situations, such as when executing software input by untrusted users, in malware analysis, or even as a security mechanism in case a trusted system gets compromised \cite{DBLP:journals/peerj-cs/MaassSCS16}.
A sandbox environment should be able to shield the host machine or operating system from any damages caused by third party software. Thus, sandbox environment should have the minimum requirements to run programs (make sure the program will not impact resources outside the sandbox), and make sure it will never assign the program greater privileges than it should have, 
working with the principle of the least privilege, giving permissions to users according to their needs, \textit{i.e.}, giving them no more power than needed to successfully perform their task. This principle prevents escalating privileges and unauthorized access to resources, thereby improving the system's overall health. Within the Android ecosystem, least privilege is realized through sandboxing process, where apps never access the data of other apps, and an app just accesses non-sensitive user resources, like contacts and location, through specific APIs (Application Programming Interface), which are in-turn guarded by permissions.

>>>>

A sandbox is an isolated environment on an electronic device within which applications cannot affect other programs outside its boundaries, like the file system, the network, or other device data. It enables testing and execution of unsafe or untested code, possible malware, without worrying about the integrity of the electronic device that runs the application. This need may arise in a variety of situations, such as when executing software input by untrusted users, in malware analysis, or even as a security mechanism in case a trusted system gets compromised \cite{DBLP:journals/peerj-cs/MaassSCS16}.
A sandbox environment should be able to shield the host machine or operating system from any damages caused by third party software. Thus, sandbox environment should have the minimum requirements to run programs (make sure the program will not impact resources outside the sandbox), and make sure it will never assign the program greater privileges than it should have, 
working with the principle of the least privilege, giving permissions to users according to their needs, \textit{i.e.}, giving them no more power than needed to successfully perform their task. This principle prevents escalating privileges and unauthorized access to resources, thereby improving the system's overall health. Within the Android ecosystem, least privilege is realized through sandboxing process, where apps never access the data of other apps, and an app just accesses user resources, like contacts and location, through specific APIs (Application Programming Interface), which are in-turn guarded by permissions.

### 2021-03-04 benchmark.tex
second general review

\begin{figure*}[ht]
  \includegraphics[width=1\textwidth]{images/benchmark3.png}
  \label{benchArq}
  \caption{Benchmark architecture}
  \label{fig:benchArq}
\end{figure*}

@@

The droidXP CLI provides two commands: a command that lists all test case
generation tools (executing the project with the option ``list-tools'') that had been
integrated into the benchmark; and a command that performs the execution of the benchmark,
which can be configured using the following parameters:

@@

The droidXP architecture relies on the pipes-and-filters architectural style \cite{architecture-book} (Figure \ref{fig:benchArq}),
and includes three main components; where each component is responsible for a specific phase of the
benchmark (instrumentation, execution, and result analysis).

@@

In the first phase, a researcher must define the corpus of APK files droidXP
should consider during a benchmark execution. After that, droidXP starts the DroidFax service that instruments each APK file, so that droidXP would be able to collect data about each execution. To improve the performance of the benchmark, the instrumentation phase runs only once for each APK. In this phase, the DroidFax tool also runs some static analysis procedures, to collect the number of methods and classes of each app, which is a necessary information to estimate code coverage.

@@

In this phase, droidXP installs an (already instrumented) APK file into
an Android emulator, and then executes a test case generation tool
during a period of time. This process repeats for every test case generation
tool and APK files. To provide repeatability of the experiment,
droidXP removes all data stored in the emulator before starting
a new execution. That is, every execution uses a \emph{fresh} emulator,
without any information that might have been kept during
previous executions.

The benchmark is relatively easy to add new test
case generation tools. To achieve this goal, it leverage the
Strategy Design pattern \cite{patterns-book}, which sets a contract between a family of classes that, in our case, abstracts the specificities for running each tool we want to integrate into droidXP. Listing \ref{lst:toolspec} shows the contract a developer must override to integrate a new tool. According to this contract, one have to: (a) implement a class that inherits from \texttt{ToolSpec}, define constructors that calls the \texttt{super} constructor, passing the name, the description, and the process id as arguments, and (c) implement the \texttt{execute} method, which receives as argument the path of an APK file and a timeout.

@@

The benchmark uses the last parameter to kill the execution process
on the emulator after a \emph{timeout event} throws.
This step is necessary to provide a fresh environment
for the next test execution. The actual logic for executing a
specific tool resides in the  \texttt{execute} method,
so it is the responsibility of a developer to
set up all configuration necessary to run a specific
test case generation tool. To performance our study replication we integrated successfully 
the following tools into droidXP.

>>>>

\begin{figure*}[ht]
  \includegraphics[width=1\textwidth]{images/benchmark4.png}
  \label{benchArq}
  \caption{Benchmark architecture}
  \label{fig:benchArq}
\end{figure*}

@@

The DroidXP CLI provides two commands: a command that lists all test case
generation tools (executing the project with the option ``list-tools'') that had been
integrated into the benchmark; and a command that performs the execution of the benchmark,
which can be configured using the following parameters:

@@

The DroidXP architecture relies on the pipes-and-filters architectural style \cite{architecture-book} (Figure \ref{fig:benchArq}),
and includes three main components; where each component is responsible for a specific phase of the
benchmark (instrumentation, execution, and result analysis).

@@

In the first phase, a researcher must define the corpus of APK files DroidXP
should consider during a benchmark execution. After that, DroidXP starts the DroidFax service that instruments each APK file, so that DroidXP would be able to collect data about each execution. To improve the performance of the benchmark, the instrumentation phase runs only once for each APK. In this phase, the DroidFax tool also runs some static analysis procedures, to collect the number of methods and classes of each app, which is a necessary information to estimate code coverage.

@@

In this phase, DroidXP installs an (already instrumented) APK file into
an Android emulator, and then executes a test case generation tool
during a period of time. This process repeats for every test case generation
tool and APK files. To provide repeatability of the experiment,
DroidXP removes all data stored in the emulator before starting
a new execution. That is, every execution uses a \emph{fresh} emulator,
without any information that might have been kept during
previous executions.

The benchmark is relatively easy to add new test
case generation tools. To achieve this goal, it leverage the
Strategy Design pattern \cite{patterns-book}, which sets a contract between a family of classes that, in our case, abstracts the specificities for running each tool we want to integrate into DroidXP. Listing \ref{lst:toolspec} shows the contract a developer must override to integrate a new tool. According to this contract, one have to: (a) implement a class that inherits from \texttt{ToolSpec}, define constructors that calls the \texttt{super} constructor, passing the name, the description, and the process id as arguments, and (c) implement the \texttt{execute} method, which receives as argument the path of an APK file and a timeout.

@@

The benchmark uses the last parameter to kill the execution process
on the emulator after a \emph{timeout event} throws.
This step is necessary to provide a fresh environment
for the next test execution. The actual logic for executing a
specific tool resides in the  \texttt{execute} method,
so it is the responsibility of a developer to
set up all configuration necessary to run a specific
test case generation tool. To performance our study replication we integrated successfully 
the following tools into DroidXP.

### 2021-03-04 conclusionfutureworks.tex
second general review

\section{conclusion and future work}

@@

In this paper, we performed two studies. In the first we conducted a non-exact replication of \blls, considering $96$ pairs apps (B/M) from the original study, and selecting $5$ test generation tools to run for $1$ minute for $2$ times. Firstly, we performed the study, using DroidXP benchmark with its default configuration, enabling the Droidfax static analysis algorithms, and repeat the study by disabling Droidfax, to compute the effective performance of the test generation tools, ignoring the influence of static analysis. For the second experiment, we complement the dynamic analysis using tainted analysis algorithms, through Flowdroid tool, over the same $96$ pairs (B/M) of the previous experiment. The results of the first experiment reveals that, ignoring our fake test case generation tool (Joker), that does not executed the apps, 51.04\%-73.95\% of the malware investigated was detected using the sandboxes with the support of Droidfax static analysis algorithms. Enabling the Droidfax, the sandoxes improved its performances from 23.94\% (Monkey) to 69.39\% (Humanoid). We also find that 19.79\% of malicious apps (19 out of 96) could be detected by none of the sandboxes generated. In the second experiment, the tainted analysis detected 58 among 96 pairs investigated (60.42\%), a better performance than any sandbox constructed by the execution of the test case tools without the Droidfax static analysis algorithms.

>>>>

\section{Conclusion and future work}

@@

In this paper, we performed two studies. In the first we conducted a replication of \blls, considering $96$ pairs apps (B/M) from the original study, and selecting $5$ test generation tools to run for $3$ minute for $3$ times. Firstly, we performed the study, using DroidXP benchmark with its default configuration, enabling the Droidfax static analysis algorithms, and repeat the study by disabling Droidfax, to compute the effective performance of the test generation tools, ignoring the influence of static analysis. For the second experiment, we complement the dynamic analysis using tainted analysis algorithms, through Flowdroid tool, over the same $96$ pairs (B/M) of the previous experiment. The results of the first experiment reveals that, ignoring our fake test case generation tool (Joker), that does not executed the apps, $58.33\%$-$76.04\%$ of the malware investigated was detected using the sandboxes with the support of Droidfax static analysis algorithms. The impact of Droidfax in the results range from $16.44\%$ (DroidBot) to $51.79\%$ (Humanoid). We also found that $18.75\%$ of malicious apps (18 out of 96) could be detected by none of the sandboxes generated. In the second experiment, the tainted analysis detected 58 among 96 pairs investigated (60.42\%). With the exception of DroidBot tool, tainted analysis algorithms had a better performance than any sandbox constructed by the execution of another test case tool, without the Droidfax static analysis algorithms. Our work show that the number of malicious behaviours detected is increased for all cases with tainted analysis aid, achieving at the best case, $82.29\%$ (79 among 96) of malware detected with DroidBot.

### 2021-03-04 results.tex
second general review

\subsection{Result of the first study: A non-exact replication}\label{sec:res-fs}

@@

Altogether, ignoring the \joke tool, our study reveals that from $58.33$\% (Humanoid)
to $76.04$\% (DroidBot) of the malicious apps investigated in our study can be
detected using the sandboxes generated after running the test case tools with the support of the
DroidFax static analysis algorithms. Besides that, in the first execution, none of the
resulting sandboxes could detect 18 malwares in our dataset ($18.75$\%). According to
the Euphony tool~\cite{hurier2017euphony}, $12$ of these $18$ malwares are \emph{adwares}, $3$ are \emph{trojans}, $2$ are
PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}.

@@

In this second study we used a tainted analysis approach to mine differences between the benign and malicious versions of each of the 96 Android apps in our dataset. To this end we leverage the FlowDroid
%\kn{ Have we cited flowdroid before. If yes, ignore my comment} 
tool, which tracks how sensitive information flows through the apps using tainted analysis algorithms. Regarding accuracy, the tainted analysis approach detected $58$ out of the $96$ pairs in our dataset ($60,42$\%), that is, the FlowDroid approach leads to a better performance than any sandbox originated in the second execution of the dynamic analysis tools (without the DroidFax static analysis algorithms).

@@

Here we present details about one of the malware that Flowdroid had detected. At this package (com.yy.fontmaster), from another alternative android market, angeeks~\cite{angeeks}, the malicious and benign apps have the same sink, however they access different sources, therefore configuring additional source-sink pairs, and hence a possible malicious behaviours. The Figure \ref{fig:sourcesink}, presents the paths source (blue border) and sink (orange border) from benign and malicious apps.

>>>>

\subsection{Result of the first study: A \blls replication}\label{sec:res-fs}

@@

Altogether, ignoring the \joke tool, our study reveals that from $58.33$\% (Humanoid)
to $76.04$\% (DroidBot) of the malicious apps investigated in our study can be
detected using the sandboxes generated after running the test case tools with the support of the
DroidFax static analysis algorithms. Besides that, in the first execution (WS), none of the
resulting sandboxes could detect 18 malwares in our dataset ($18.75$\%). According to
the Euphony tool~\cite{hurier2017euphony}, $12$ of these $18$ malwares are \emph{adwares}, $3$ are \emph{trojans}, $2$ are
PUPs (\emph{Potentially Unwanted Program}), and one is an \emph{exploit}.

@@

In this second study we used a tainted analysis approach to mine differences between the benign and malicious versions of each of the 96 Android apps in our dataset. To this end we leverage the FlowDroid
%\kn{ Have we cited flowdroid before. If yes, ignore my comment} 
tool, which tracks how sensitive information flows through the apps using tainted analysis algorithms. Regarding accuracy, the tainted analysis approach detected $58$ out of the $96$ pairs in our dataset ($60,42$\%), that is, the FlowDroid approach leads to a better performance than three sandbox originated in the second execution of the dynamic analysis tools (without the DroidFax static analysis algorithms), losing only to sandbox build by Droidbot, that detected $61$ out of the $96$ pairs ($63,54$\%)

@@

Here we present details about one of the malware that Flowdroid had detected. At this package \texttt{com.yy.fontmaster}, from alternative android market, angeeks~\cite{angeeks}, the malicious and benign apps have the same sink, however they access different sources, therefore configuring additional source-sink pairs, and hence a possible malicious behaviours. The Figure \ref{fig:sourcesink}, presents the paths source (blue border) and sink (orange border) from benign and malicious apps.

### 2021-03-04 setup.tex
revision for jounal - background - result
second general review

We investigate the four test case generation tools described earlier and added a fake test
case generation tool (named Joker) that simulates a test tool that does not execute
the Android apps during a benchmark execution. Using this tool, the results
of the dynamic analysis are not considered and we can compute the results with
only the static analysis component of DroidFax (RQ1). Our study executed each pairs of
Android app (B/M) in each one of the five test generation tools, including Joker,
for three minutes, and for three times. We then investigate the performance of each tool to detect malicious behaviors in the sandbox modeled by the test generation tool
under analysis. Figure \ref{fig:setup} shows this experimental setup.

@@

After that, we replicated the study using a configuration of DroidXP that disables the DroidFax static analysis algorithm. With this new configuration, we executed the benchmark again, using the same dataset of Android pairs apps, the same execution time, and the same test case generation tools.
The results of this replication allow us to compute the effective performance
of the dynamic analysis tools (RQ2)---that is, ignoring the influence of the
DroidFax static analysis algorithms.

@@

To complement our initial study, we performed the tainted analysis at the same
data set from the first study. For this second study, we used
FlowDroid~\cite{10.1145/2666356.2594299}, a static flow analysis tool for Android apps.
The goal is to test accuracy of static analysis, through tainted analysis algorithms, at finding malicious behavior, and compare the results with previous study at the same data set.
In this second study, a behavior is considered malicious whenever the algorithms
detected a different set of source-sink pairs, coming from the benign and malign
versions of an Android app.

>>>>

We investigate the four test case generation tools described earlier and added a fake test
case generation tool (named Joker) that simulates a test tool that does not execute
the Android apps during a benchmark execution. Using this tool, the results
of the dynamic analysis are not considered and we can compute the results with
only the static analysis component of DroidFax (RQ1). Our study executed each pairs of
Android app (B/M) in each one of the five test generation tools, including Joker,
for three minutes, and for three times. We then investigate the performance of each tool to detect malicious behaviors in the sandbox modeled by the test generation tool
under analysis.

@@

After that, we replicated the study using a configuration of DroidXP that disables the DroidFax static analysis algorithm. With this new configuration, we executed the benchmark again, using the same dataset of Android pairs apps, the same execution time, and the same test case generation tools.
The results of this replication allow us to compute the effective performance
of the dynamic analysis tools (RQ2)---that is, ignoring the influence of the
DroidFax static analysis algorithms. Figure \ref{fig:setup} shows all the phases of our experimental, that explore all sensitive resources access by both apps (B/M), and the optional configuration DroidXP, that disables Droidfax static analysis.

@@

To complement our initial study, we performed the tainted analysis at the same
data set from the first study. For this second study, we used
FlowDroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14}, a static flow analysis tool for Android apps.
The goal is to test accuracy of static analysis, through tainted analysis algorithms, at finding malicious behavior, and compare the results with previous study at the same data set.
In this second study, a behavior is considered malicious whenever the algorithms
detected a different set of source-sink pairs, coming from the benign and malign
versions of an Android app.
